Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Show wake profiles to quantify wake differences; resolves #57

These same wake maps were measured for $Re_D = 0.4 \times 10^6$, $0.6 \times
10^6$, $0.8 \times 10^6$, and $1.2 \times 10^6$. Qualitatively, these look
strikingly similar, so they have not been plotted here. We will instead compare
and contrast the wake behavior by examining spectra and wake transport terms in
the equations that govern the downstream evolution of mean momentum and kinetic
energy.

@@

>>>>

These same wake maps were measured for $Re_D = 0.4 \times 10^6$, $0.6 \times
10^6$, $0.8 \times 10^6$, and $1.2 \times 10^6$. Qualitatively, these look very
similar, so they have not been plotted here, though profiles at $z/H=0.0$ are
shown in Figure~\ref{fig:profiles} to illustrate the subtlety of the
differences. We will instead compare and contrast the wake behavior by examining
spectra and wake transport terms in the equations that govern the downstream
evolution of mean momentum and kinetic energy.

@@

    \includegraphics[width=0.85\textwidth]{figures/mean_u_k_profiles}

    \caption{Mean streamwise velocity (left) and turbulence kinetic energy
        (right) profiles at $z/H=0.0$. Legend indicates $Re_D$.}

    \label{fig:profiles}
\end{figure}
